---
title: "EDRM 718 Assignment 9"
author: "Michael and Mike"
date: "10 April 2020"
output: html_notebook
---

This is a study of the relationship of income to ethnicity using a sample of
American workers. In this study I want to determine if there is a difference
in the average income of workers of different ethnic backgrounds after 
adjusting for years of education.

```{r include=FALSE}

library(tidyverse)

inc_data <- read_csv("Ethnic Income Data.csv")

inc_data$Race <- factor(inc_data$Race,
                        levels = c("b", "h", "w"),
                        labels = c("Black", "Hispanic", "White"))

```


### Descriptive Comparison of Income

These are boxplots that show differences in income by ethnicity **without**
adjusting for the years of education.

```{r}

boxplot(inc_data$Income ~ inc_data$Race, ylim = c(0, 120), xlab = "Race",
        ylab = "Income (in $1000)", main = "Income by Race")

```

Here are the five-number summaries and means for the ethnic group incomes.

```{r}

tapply(inc_data$Income, inc_data$Race, summary)

```

Here are the standard deviations for the ethnic group incomes.

```{r}

tapply(inc_data$Income, inc_data$Race, sd)

```

This is a plot to look at the difference in income for the race categories 
while taking into account years of education.

```{r}

plot(inc_data$Income ~ inc_data$Educ, pch=as.numeric(inc_data$Race),
     col=as.numeric(inc_data$Race), xlab = "Years of Education",
     ylab = "Income (in $1000)", main = "Income as a Function of Education by        Race")

legend("topleft", inset = .05, legend = c("Black", "Hispanic", "White"),
       title = "Race", pch = c(1:3), col = c(1:3), cex = .7)

```



This is a check for interaction.

```{r}
# Now let's check for interaction.

model1 <- inc_data$Income ~ inc_data$Educ * inc_data$Race
model1.out <- lm(model1)
anova(model1.out)

```

